A molecular taxonomy of tumors independent of tissue-of-origin

### 2020-08-26 text/manuscript.Rmd
last minit typos and fixes (DH)

**Figure 2: Clustering of tumor samples** Different rotational perspectives of
the same MCA-based UMAP projection in three-dimensional space. Each dot
corresponds to a tumor sample. The same colors indicate the tumor's cluster
identity throughout this manuscript. 1=yellow, 2=lilac, 3=orange, 4=light blue,
5=crimson, 6=beige, 7=grey, 8=dark green, 9=pink, 10=dark blue.

@@

Finally, as a measure of tumor advancement, metastasis is the condition in which
certain phenotypic criteria are met. These phenotypes include (among others)
loss of differentiation, cell-cell contacts, epithelial to mesenchyme
transition, immune system evasion and tissue invasiveness [@hallmarks_II]. To
determine whether any of our clusters correspond to an especially advanced stage
of cancer across tissue types, we projected the metastasis data onto our UMAP,
and surprisingly we observed an even distribution of metastases across classes
(**figure 3E**). This final observation suggests that our pathway-disruption
classification is dependent on particular combinations of gene mutations
affecting different pathways that can each give rise to advanced stages of
disease and metastasis, regardless and independent of overall mutational burden
(see Discussion for further analysis).

>>>>

**Figure 2: Clustering of tumor samples** Different rotational perspectives of
the same MCA-based UMAP projection in three-dimensional space. Each dot
corresponds to a tumor sample. The same colors indicate the tumor's cluster
identity throughout this manuscript.

@@

Finally, as a measure of tumor advancement, metastasis is the condition in which
certain phenotypic criteria are met. These phenotypes include loss of
differentiation, cell-cell contacts, epithelial to mesenchyme transition, immune
system evasion and tissue invasiveness [@hallmarks_II]. To determine whether any
of our clusters correspond to an especially advanced stage of cancer across
tissue types, we projected the metastasis data onto our UMAP, and surprisingly
we observed an even distribution of metastases across classes (**figure 3E**).
This final observation suggests that our pathway-disruption classification is
dependent on particular combinations of gene mutations affecting different
pathways that can each give rise to advanced stages of disease and metastasis,
regardless and independent of overall mutational burden.
